Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
space in lists

\vspace{1ex}
\noindent\textbf{Technical Factors} We collected technical factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

@@

\begin{itemize}
\item Repositories: a count of the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

>>>>

\vspace{1ex}
\noindent\textbf{Technical Factors} We collected technical factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Source lines of source code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

\begin{itemize}
\item Repositories: number of repositories the developer can access, including those
the developer owns, contributes
to, and for which the developer has organizational membership access.%
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}
